Staged Abstract Interpreters

### 2019-03-25 paper/30_stageconc.tex
misc

Readers may notice that the conversion between unstaged monads and monads is 
simply changing the unstaged data to staged data, which in fact can be achieved without
changing the implementation of monads. This is true so far, but as will see in
the abstract interpreter when introducing the nondeterminism monad (@ListT@), as
the whole list will be a next-stage value instead of merely the elements in the list.
For this reason, we explicitly distinguish and present the two version of
monads, as a more consistent approach.

>>>>

Readers may notice that the conversion between unstaged monads and monads is 
simply changing the unstaged data to staged data, which in fact can be achieved without
changing the implementation of monads. This is true so far, but as we will see
when introducing the nondeterminism monad (@ListT@) for abstract interpreters, as
the whole list will be a next-stage value instead of merely the elements in the list.
For this reason, we explicitly distinguish and present the two version of
monads, as a more consistent approach.
